Estimating Uncertainty for Tipping Points with Deep Learning

### 2022-05-13 manuscript/manuscript.Rmd
add means

```{r}
shift |> 
  ggplot(aes(forecasting_model, score, color=forecasting_model)) + 
  geom_jitter(alpha = 0.06, show.legend = FALSE, shape=".") + 
  coord_flip() +
  facet_grid(simulation ~ metric, scales = "free") + 
  scale_y_log10() +
  theme_bw()

>>>>

```{r}
shift |> 
  ggplot(aes(forecasting_model, score, color=forecasting_model)) + 
  #geom_boxplot(col="black", outlier.size=0, outlier.shape = ".", outlier.alpha=0) +
  geom_jitter(alpha = 0.06, show.legend = FALSE, shape=".") + 
  stat_summary(fun = mean, shape="|", show.legend = FALSE, col="black") +
  coord_flip() +
  facet_grid(simulation ~ metric, scales = "free") + 
  scale_y_log10() +
  theme_bw()
